---
title: "Intro_Statistics_Computing_01"
author: "MinJi Kim"
date: '2023-03-06'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

### Arithmatic with R
```{r}
# An addition
15 + 5

# A subtraction
15 - 5

# A multiplication
3 * 5

# A division
(15 + 5) / 2

# Exponentiation
2^4

# Modulo (나머지)
32%%6
```

### Basic data types in R
```{r}
# Assign numeric to be 20
numeric = 20

# Assign character to be "SKKU"
character <- "SKKU"

# Assign logical to be TRUE
logical = TRUE

# Check class of numeric
class(numeric)

# Check class of character
class(character)

# Check class of logical
class(logical)
```

### Create a vector
```{r}
seq(5)

1:5

seq(-3,0, by=0.5)

rep(2,5)

a = seq(-1,0, by=0.5)
a

rep(a,3)

rep(seq(-1,0, by=0.5), 3)

b = c(1,2,3)
b

c(a,b)

a = seq(-1,0, by=0.2)
a
a[2]
a[3:5]
a[c(1,3,4)]
```

### Create a matrix
```{r}
matrix(1:10, nrow=5, byrow = T)
matrix(1:10, nrow=5, byrow = F)

matrix(0, nrow=2, ncol=3)
array(0,c(2,3)) # array(배열)는 matrix(행렬)를 쌓아올린 것

diag(2,4)
diag(diag(1,4))
# diag() 함수에 벡터를 넣으면, 벡터의 원소를 대각선원소로 갖는 대각행렬을 만든다. 반면에 diag() 함수에 행렬을 넣으면 반대로 대각선원소를 반환한다.
```

### Column/Row binding
```{r}
a=diag(2,4); b=1:4
cbind(a,b) # column binding
rbind(a,b) # row binding
```

### Create a submatrix
```{r}
a=array(c(1:5, rep(2,3), c(-2,-5,3,10)), c(3,4)); a
a[1:2, c(1,4)] # [행,열] ==> 1,2행과 1,4열의 값을 인덱싱하여 반환함.
```

### Create a matrix (example)
```{r}
set.seed(2018)
score=matrix(runif(12,50,100), ncol=3) # runif(n,min,max) 난수 생성함수
dimnames(score)[[1]]=c("John", "David", "Xuming", "Zhao") # matrix의 행에 이름 설정
dimnames(score)[[2]]=c("Math", "English", "Science") # matrix의 열에 이름 설정
score

round(score,2) # round score off to 2 decimal places

score["Xuming", "English"] # 행열 인덱스 명으로 값 searching 가능
score[, score[3,]>70] # 인덱스 내에 조건 걸어주기 가능
```

### Determinant of a matrix
```{r}
set.seed(2012)
A=matrix(rnorm(16,mean=0,sd=1), nrow=4)
det(A)
solve(A)
```

### Eigenvalues of matrices
##### For a matrix A, \lambda is an eigenvalue of A if it holds $Ax = \lambda x$ for some $x \neq 0$.
##### This is equivalent to satisfying $(A - \lambda I)x = 0$ for some $x \neq 0$, i.e. $det(A - \lambda I) = 0$.
##### The follwing are equivalent:
#####  (a) A is invertible
#####  (b) All eigenvalues of A are nonzero
#####  (c) $det(A) \neq 0$
```{r}
eigen(A)$values
```


##### If A is a symmetric matrix, then all eigenvalues of A are real numbers.
```{r}
B=(A+t(A))/2
B
eigen(B)$values
```

### Invertible matrix
##### Suppose A and B are the same dimensional invertible matrices. Then
##### (a) (A^-1^)^T^ = (A^T^)^-1^
##### (b) (A^-1^)^-1^ = A
##### (c) (AB)^-1^ = B^-1^A^-1^
##### (d) (AB)^T^ = B^T^A^T
##### (e) $1/\lambda ~j~(A)$ is an eigenvalue of A^-1^
##### (f) A and A^-1^ have the same eigenvectors
```{r}
set.seed(2018)
A=matrix(runif(16,0,10), ncol=4); A = (A + t(A))/2
B=matrix(runif(16,0,10), ncol=4); B = (B + t(B))/2
```


### Learning "for" with a Taylor series
```{r}
x = 5
n = 100

Taylor_sum = 0
for (i in 0:n){
  Taylor_sum = Taylor_sum+x^i
}

round(Taylor_sum,3)
round(1/(1-x),3) # The random number doesn't satisfy

# Consider any number in (-1,1).
x = 0.5
n = 100

Taylor_sum = 0
for (i in 0:n){
  Taylor_sum = Taylor_sum + x^i
}

round(Taylor_sum,3)
round(1/(1-x),3) # The random number does satisfy
```

### Create a function
```{r}
check_conv <- function(x,n){
  Taylor_sum_series = NULL; err_set = NULL
  Taylor_sum = 1
  for (i in 1:n){
    Taylor_sum = Taylor_sum + x^i
    err = abs(1/(1-x) - Taylor_sum)
    Taylor_sum_series = c(Taylor_sum_series,Taylor_sum)
    err_set = c(err_set, err)
  }
  return(list(Taylor_sum_series = Taylor_sum_series, err_set = err_set))
}

# Run the function "check_conv"
x = 0.8
n = 100
result = check_conv(x,n)
summary(result)

set.seed(2018)
result$Taylor_sum_series
result$err_set
result$Taylor_sum_series[96:100]
round(result$err_set[96:100],3)
```

### Create a plot
```{r}
errs = result$err_set
plot(1:length(errs), errs, type="b", col="blue", main="Taylor series errors", xlim=c(1,50))
```

### Learning "while" with Taylor series
```{r}
x = 0.2

# initial setting
Taylor_sum = 1; err = 100; i = 0; err_set = NULL

while(err >= 10^(-7)){
  i = i+1
  Taylor_sum = Taylor_sum + x^i
  err = abs(1/(1-x) - Taylor_sum)
  err_set = c(err_set, err)
}

length(err_set)
err_set
```

### Learing "if" with Taylor series
```{r}
x = 0.7

# initial setting
Taylor_sum = 0; err = 100; i = 0; err_set = NULL

while(err >= 10^(-10)){
  i = i + 1
  Taylor_sum = Taylor_sum + (-1)^(i+1) * x^(2*i-1) / factorial(2*i-1)
  err = abs(sin(x) - Taylor_sum)
  err_set = c(err_set,err)
}

# The number of required iterations
i

# Error set
err_set

# use "if" function
x = 0.7
Taylor_sum = 0; err_set = NULL

for(i in 1:10000){
  Taylor_sum = Taylor_sum + (-1)^(i+1) * x^(2*i-1) / factorial(2*i-1)
  err = abs(sin(x) - Taylor_sum)
  err_set = c(err_set,err)
  if (err < 10^(-10)){
    break
  } else if (err >= 10^(-10) & err < 10^(-5)){
    print("Almost done!")
  } else {
    print("More iterate!")
  }
}

# The number of required iterations
i

err_set

# Save "i" and "err_set"
save(i, err_set, file="your_name_ID_exercise1")

# Load the saved data file
load("your_name_ID_exercise1")
```

